Research log

### 2023-01-19 analysis/decisionConformityBattleship.Rmd
decision conformity analysis

---
title: "Decision entropy"
author: "Matan Mazor"
date: "2023-01-18"
output: html_document
---

@@

#compute Shannon entropy
entropy <- function(target) {
  freq <- table(target)/length(target)
  # vectorize
  vec <- as.data.frame(freq)[,2]
  #drop 0 to avoid NaN resulting from log2
  vec<-vec[vec>0]
  #compute entropy
  -sum(vec * log2(vec))
}

@@

E2.click_entropy_by_serial_position_summary <- E2.click_entropy_by_serial_position %>%
  group_by(test_part,click_number) %>%
  summarise(mean_entropy=mean(entropy),
            se_entropy=se(entropy)) %>%
  mutate(test_part = factor(test_part, levels=c('nonpretend','pretend','random','optimal')));

@@

ggsave('../figures/E2_entropy_by_click_nnumber.png',p,width=5,height=5,dpi=300)

>>>>

---
title: "Decision conformity: Battleship"
author: "Matan Mazor"
date: "2023-01-18"
output: html_document
---

@@

#compute Shannon entropy, but only until the first timepoint at which some gamed ended
entropy <- function(target) {
  if (length(target)<5) {
    return(NaN)
  } else {
    freq <- table(target)/length(target)
    # vectorize
    vec <- as.data.frame(freq)[,2]
    #drop 0 to avoid NaN resulting from log2
    vec<-vec[vec>0]
    #compute entropy
    return(-sum(vec * log2(vec)))
  }
}

@@

E2.click_entropy_by_serial_position_summary <- E2.click_entropy_by_serial_position %>%
  group_by(test_part,click_number) %>%
  summarise(mean_entropy=mean(entropy, na.rm=T),
            se_entropy=se(entropy, na.rm=T)) %>%
  mutate(test_part = factor(test_part, levels=c('nonpretend','pretend','random','optimal')));

@@

ggsave('../docs/figures/E2_entropy_by_click_nnumber.png',p,width=7,height=5,dpi=300)

### 2023-01-19 researchLog.Rmd
decision conformity analysis

---
title: "Research log"
author: "Matan Mazor"
date: "2023-01-18"
output: github_document
bibliography: references.bib
---

@@

>>>>

---
title: "Research log"
author: "Matan Mazor"
date: "2023-01-18"
output: github_document
---

@@

## Analysis of decision conformity (2023-01-19)

Part of the solution to the problem is that entropy decreases when there are fewer possible events, and that happens when the click number is high enough such that some games have already ended. When restricting the analysis only to cases in which the games haven't ended yet, entropy remains high. But for some reason it does decrease for the random and optimal agents:

![](docs/figures/decision_entropy_with_stars.png){width="615"}

It might be subjects that go over the board systematically that decrease this measure.

The important thing is that early on, entropy seems to be higher for nonpretend games.

Oddly, the difference is already apparent in the first click 🤔
